### 2014-04-06 paper/discussion.tex
mmodz
george comments
minor tweaks

@@

By crossing pipe types, topologies, and inserted media, many pipe-mediated interactions emerge. We demonstrated a few such possibilities by designing and fabricating example objects with the help of our pipe routing design tool. However, there are many additional possibilities for leveraging sensing and actuation techniques from the HCI literature and extending their use in 3D-printed objects. We briefly survey such possibilities for output and input.

@@

=======
>>>>>>> bd673f22cceca8b1cbc4a00aae3717eacd7fd9f2
\bjoern{We might pull back on the scope of this section a bit and think about which directions here are most closely related to pipes and most likely successful;  and which are more tangential or speculative - for example, Aireal is about feedback in free space and we are all about designing tangible objects; so maybe that's a candidate for cutting.}

@@

>>>>

\valkyrie{there are a lot of things in here that we could focus on.  input/output/identity interactions mediated by tubes, the creation of antennae and other custom electronics...}

\valkyrie{which figures/discussions do we think are important?}

@@

\begin{figure}[h]
\centering
    \includegraphics[width=3.4in]{figures/electronics.png}
\caption{(a) A capacitor we manufactured on a 3D printer and coated, post-print, with copper paint.  This particular one holds a charge of xx.  (b) Comparison of theoretical printed resistors.  For a cylindrical wire, resistance = $\rho\frac{l}{\pi r^2}$, where $\rho$ is based on the conductivity of the medium.  In our case, assuming $ r << l$, resistance(B) < resistance(C) < resistance(A).  (c) A possible design for a cell phone antenna augmentation inside a cell phone case.}
\label{fig:electronics}
\end{figure}

These internal designs can give rise to new opportunities in electronics design and fabrication: we printed a proof-of-concept printed capacitor which features a thin printed plate with hollow cones on either side (see Figure \ref{fig:electronics}A).  After printing, we coated the inner surfaces of capacitor with copper paint.  It now can hold a charge of xx.  Similarly, tubes can be used to create \emph{resistors} in ``printed'' circuitry: a longer or thinner tube has a greater resistance than a shorter or wider one (see Figure \ref{fig:electronics}B).  Internal \emph{antenna} design is also possible, which could lead to new flexibility in, e.g., cell phone design (see Figure \ref{fig:electronics}C).

By crossing pipe types, topologies, and inserted media, many pipe-mediated \emph{interactions} also emerge. We demonstrated a few such possibilities by designing and fabricating example objects with the help of our pipe routing design tool. However, there are many additional possibilities for leveraging sensing and actuation techniques from the HCI literature and extending their use in 3D-printed objects. We briefly survey such possibilities for output and input.

@@

\bjoern{We might pull back on the scope of this section a bit and think about which directions here are most closely related to pipes and most likely successful;  and which are more tangential or speculative - for example, Aireal is about feedback in free space and we are all about designing tangible objects; so maybe that's a candidate for cutting.}

@@

\valkyrie{do we want those figures of the helmholz thing and the servo redirection gate?}

### 2014-04-06 paper/introduction.tex
minor tweaks

\begin{figure}[h]
\centering
    \includegraphics[width=3.4in]{figures/placeholder/teaser.png}
\caption{A collection of interactive objects designed using our tool.  All have electronic sensing or actuation components which are routed through the \emph{interior} of the prints to preserve aesthetics.  In (a), objects manufactured on a hobbyist 3D printer.  In (b), those manufactured on industrial-grade printers.}
\label{fig:teaser}
\end{figure}

\section{Introduction}
Makers, as well as professional designers, leverage 3D printers as tools for design work.  A wide array of objects, ranging from bicycle helmets to video game controllers, are now prototyped or even manufactured using these machines.  However, most devices fabricated by 3D printers are passive, prototyping the form, but not the interactivity, of an object.

@@

We propose a novel technique involving the removal of material from the interior of 3D models, prior to printing, to create pipes and other cavities.  These pipes can be filled, post-print, by a variety of media that enable input, display, and tactile feedback.  This {\em subtractive} approach is complementary to {\em additive} approaches that inject custom print materials, such as conductors, during the actual printing process [ref]. While our approach requires some manual assembly after a print completes, it gives makers the opprotunity to cheaply and rapidly prototype a diverse range of interactive objects on 3D printers, including hobbyist machines (Figure \ref{fig:teaser}).

>>>>

\begin{figure}[h]
\centering
    \includegraphics[width=3.4in]{figures/placeholder/teaser.png}
\caption{A collection of interactive objects designed using our tool.  All have electronic sensing or actuation components which are routed through the \emph{interior} of the prints to preserve aesthetics.  In (a), objects manufactured on a hobbyist 3D printer.  In (b), those manufactured on industrial-grade printers. \valkyrie{once these photos are taken, we could expand this into a full-page-span figure that hopefully makes everything look exciting and awesome}}
\label{fig:teaser}
\end{figure}

\section{Introduction}
Makers, as well as professional designers, leverage 3D printers as tools for design work.  A wide array of objects, ranging from bicycle helmets to video game controllers, are now prototyped or even manufactured using these machines.  However, most devices fabricated by 3D printers are passive: prototyping the form, but not the interactivity, of an object.

@@

We propose a novel technique involving the removal of material from the interior of 3D models, prior to printing, to create pipes and other cavities.  These pipes can be filled, post-print, by a variety of media that enable input, display, and tactile feedback.  This {\em subtractive} approach is complementary to {\em additive} approaches that inject custom print materials, such as conductors, during the actual printing process \cite{Sells-reprap}. While our approach requires some manual assembly after a print completes, it gives makers the opportunity to cheaply and rapidly prototype a diverse range of interactive objects on 3D printers, including hobbyist machines (Figure \ref{fig:teaser}).
